%!TEX root = ../research_proposal.tex

\chapter{An Aggregate Bug Repository for Developers and Researchers\label{chap:bumper}}

In this chapter, we present {\tt BUMPER} (BUg Metarepository for dEvelopers and Researchers).
The role of {\tt BUMPER} is to aggregate information belonging to the version control and project management systems.
{\tt BUMPER} acts as our consolidated dataset.

The materials presented in this chapter are based on the following publications:

\begin{itemize}
	\item Nayrolles, M. \& Hamou-Lhadj, W. BUMPER: A Tool to Cope with Natural Language Search of Millions Bugs and Fixes. In Proceeding of the International Conference on Software Analysis, Evolution, and Reengineering (SANER'16) - Tool Track, pages 649-652, 2016.
	\item Nayrolles, M. \& Hamou-Lhadj, W. BUMPER: Bug Metarepository Search Engine for Developers and Researchers. Consortium for Software Engineering Research Fall, 2015.
\end{itemize}

\input{methodology/methodology_bumper}

\chapter{JCHARMING: Java CrasH Automatic Reproduction by directed Model checkING\label{chap:jcharming}}

In this chapter, we present {\tt JCHARMING} (Java CrasH Automatic Reproduction by directed Model checkING).
{\tt JCHARMING} is an approach to reproduce field-crash.
Every time a bug report is submitted to a project management system and aggregated by {\tt BUMPER}, {\tt JCHARMING} will try to reproduce it.
In case of success, the steps to reproduce the bug are saved in {\tt BUMPER}.

The materials presented in this chapter are based on the following publications:

\begin{itemize}
	\item Nayrolles, M. , Hamou-Lhadj, W., Tahar, S. & Larsson, A. (2016). A Bug Reproduction Approach Based on Directed Model Checking and Crash Traces. Journal of Software: Evolution and Process. Wiley. 2016. (Accepted).
	\item Nayrolles, M. , Hamou-Lhadj, W., Tahar, S. & Larsson, A. JCHARMING : A Bug Reproduction Approach Using Crash Traces and Directed Model Checking. In Proceeding of the International Conference on Software Analysis, Evolution, and Reengineering (SANER'15), pages 101-110, 2015. (Best Paper Award).
\end{itemize}

\input{methodology/methodology_jcharming}

\chapter{Preventing Clone Insertion\label{chap:clone-detection-pragmatic}}

The adoption of tools and processes that aim to support human maintainers during maintenance is relatively low \cite{Lewis2013,Foss2015,Layman2007,Ayewah2007,Ayewah2008,Johnson2013,Norman2013, Lopez2011}.
Human maintainers agree that such tools are beneficial, but, in addition of disrupting their workflow, these tools tend to have a high false positive rate.
Also, the way in which the warnings are presented, among other things, are barriers to use\cite{Johnson2013}.
When asked for their opinions, human maintainers agree to the following characteristics for maintenance-oriented tools\cite{Hovemeyer2004, Lopez2011, Lewis2013}:

\begin{itemize}
	\item Actionable messages. Presenting a warning about bug-proneness of a given line is not enough.
	Clear actions to improve the source code should be provided
	\item Obvious reasoning. The conditions that led to a given warning should be understandable by the maintainer.
	If the conditions are hidden in complex statistical models, then maintainers cannot review them and will find it difficult to trust the tool.
	\item Scaling. Industrial sized project contains thousand files and dependencies which can be updated many times a day.
	Maintenance-oriented tools should not hinder the productivity of maintainers.
	\item Contextualization. Warnings and messages should always be contextualized with respect to the project at hand and not generic rules.
	\item Integration. Developers and maintainers are overwhelmed by the amount of existing tools.
	Yet, their daily use three different kinds of tools.
	An integrated development environment, a versioning system and a project tracking system to produce, version and manage their software, respectively.
	Maintenance-oriented tools should fit in the existing ecosystem rather than complexifying the deployment process.
\end{itemize}

In this chapter, we present {\tt PRECCINT} (PREventing Clones INsertion at Commit Time) and {\tt RESEMBLE} (REcommendation System based on cochangE Mining at Block LEvel) that have the characteristics described by human maintainer.

\input{methodology/methodology_precinct}

\\
Using the block extracted by {\tt PRECINCT}, we can recommend actions to the developer.
To do so, we plan to build {\tt RESEMBLE}.
{\tt RESEMBLE} is presented in the next section.


\input{methodology/methodology_ressemble}

In summary, using {\tt PRECINCT} and {\tt RESSEMBLE} we are able to provide contextualized and accurate information in a non-intrusive manner.

\chapter{Preventing Bug Insertion Using Clone Detection}

\input{methodology/methodology_bianca}

\chapter{A taxonomy to classify the research\label{chap:taxonomy}}

\input{methodology/methodology_taxo}
